On Math

### 2025-04-23 cards/paper.tex
more updates:
- law of sines
- rational roots theorem
- intersection of a reciprocal function and a straight line
- domain of reciprocal transformed function

\documentclass{article}
\usepackage{amsmath,amssymb,amsthm,textcomp}

@@

@@

@@

@@

\subsection{Reciprocal functions}
\begin{equation}
  f(x) = \frac{1}{x}
\end{equation}
\subsection{Exponential functions}
\subsection{Logarithmic functions}
\section{Statistics}
\subsection{Linear coefficient}
Signed with $\rho$ (Greek letter called 'rho').
- $\rho = 1$ means perfect positive correlation
- $\rho = -1$ means perfect negative correlation
- $\rho = 0$ no (linear) correlation
\section{Logarithms}
\begin{table}[htbp]
\centering
\begin{tabular}{|l|l|}
\hline
\textbf{Property} & \textbf{Formula} \\
\hline
Product Rule & $\log_a(xy) = \log_a(x) + \log_a(y)$ \\
\hline
Quotient Rule & $\log_a\left(\frac{x}{y}\right) = \log_a(x) - \log_a(y)$ \\
\hline
Power Rule & $\log_a(x^n) = n \cdot \log_a(x)$ \\
\hline
Change of Base & $\log_a(x) = \frac{\log_b(x)}{\log_b(a)}$ \\
\hline
Equating arguments & $\log_af(x) = log_ag(x)$ is the same as $f(x) = g(x)$ \\
\hline
\end{tabular}
\caption{Fundamental Properties of Logarithms}
\label{tab:log_properties}
\end{table}

@@

\section{Derivatives}
Average rate of change of the function $f(x)$ on the interval $[a, a+h]$

@@

\section{Integrals}
Also called \textit{antiderivatives}. To represent integrals

@@

>>>>

\documentclass{article}
\usepackage{amsmath,amssymb,amsthm,textcomp,mathtools}

@@

\subsection{Law of sines}
% TODO: image needed

\begin{equation}
  \frac{a}{\sin A} = \frac{b}{\sin B} = \frac{c}{\sin C}
\end{equation}

and also:

\begin{equation}
  \frac{\sin A}{a} = \frac{\sin B}{b} = \frac{\sin C}{c}
\end{equation}

When we have obtuse angle we need to subtract the result from $180$.

@@

\subsection{Rational roots theorem}
Support the rational number $\frac{p}{q}$ in lowest terms, is a root of a polynomial
with integer coefficient.
% TODO: add colors to differentiate
Then 'p' must be the factor of the polynomial's constant term, and 'q' must be a factor
of its leading coefficient.
Given a polynomial with integer coefficient, any rational roots of the polynomial must take the
form:
\begin{equation}
  \pm \frac{factor of the constant term}{factor of the leading coefficient}
\end{equation}

For example:
\begin{equation}
  f(x) = 8x^3 + 12x^2 + 6x + 2
\end{equation}
so we have 16 possible roots:
\begin{equation}
  \begin{gathered}
    % TODO: strike through
    \pm \frac{1}{1}, \pm \frac{1}{2}, \pm \frac{1}{4}, \pm \frac{1}{8}, \\
    \pm \frac{2}{1}, \pm \frac{2}{2}, \pm \frac{2}{4}, \pm \frac{2}{8}
  \end{gathered}
\end{equation}

Removing the duplicates, we have 10 possible rational roots:
\begin{equation}
  \pm \frac{1}{8}, \pm \frac{1}{4}, \pm \frac{1}{2}, \pm 1, \pm 2
\end{equation}

Note: it is about 'possible' rational roots.

@@

\subsection{Intersection of a reciprocal function and a straight line}
There are three possibilities when considering the intersection of a reciprocal
function and a straight line:
1. there are two intersection points
2. there is only one intersection point
3. there are no intersection points at all

% TODO: needs images

Typically, when computing the points of intersection of a reciprocal
function and a line, we have to solve a system of two equations.

% TODO: needs bracket over two first lines
\begin{equation}
  \begin{gathered}
    y = x \\
    y = \frac{1}{x} \\
    x = \frac{1}{x} \\
    x^2 = 1 \\
    x = \pm 1
  \end{gathered}
\end{equation}

@@

\subsection{Reciprocal functions}
\begin{equation}
  f(x) = \frac{1}{x}
\end{equation}

% TODO: not range?
Domain of (transformed) reciprocal function
\begin{equation}
f(x) = \frac{a}{bx+c} + d
\end{equation}
has the horizontal asymptote $y = d$ therefore the range is
\begin{equation}
f(x) = \in (-\infty, d) \cup (d, \infty)
\end{equation}

% TODO: range
Range of (transformed) reciprocal function
\begin{equation}
f(x) = \frac{a}{bx+c} + d
\end{equation}
has the vertical asymptote $y = d$ therefore the range is
\begin{equation}
f(x) = \in (-\infty, d) \cup (d, \infty)
\end{equation}

\subsection{Exponential functions}
\subsection{Logarithmic functions}
\section{Statistics}
\subsection{Estimating a mean and variance}
\subsection{Sum of squares}
\subsection{Linear coefficient}
Signed with $\rho$ (Greek letter called 'rho').
- $\rho = 1$ means perfect positive correlation
- $\rho = -1$ means perfect negative correlation
- $\rho = 0$ no (linear) correlation
\section{Logarithms}
\begin{table}[htbp]
\centering
\begin{tabular}{|l|l|}
\hline
\textbf{Property} & \textbf{Formula} \\
\hline
Product Rule & $\log_a(xy) = \log_a(x) + \log_a(y)$ \\
\hline
Quotient Rule & $\log_a\left(\frac{x}{y}\right) = \log_a(x) - \log_a(y)$ \\
\hline
Power Rule & $\log_a(x^n) = n \cdot \log_a(x)$ \\
\hline
Change of Base & $\log_a(x) = \frac{\log_b(x)}{\log_b(a)}$ \\
\hline
Equating arguments & $\log_af(x) = log_ag(x)$ is the same as $f(x) = g(x)$ \\
\hline
\end{tabular}
\caption{Fundamental Properties of Logarithms}
\label{tab:log_properties}
\end{table}

@@

\section{Derivatives}
Average rate of change of the function $f(x)$ on the interval $[a, a+h]$:

@@

\subsection{Differentiation of an exponent function}
\begin{equation}
  \frac{d}{dx} (a^x) = a^x\ln a
\end{equation}
with special case:
\begin{equation}
  \frac{d}{dx} (e^x) = e^x\ln e = e^x * 1 = e^x
\end{equation}
\subsection{Chain rule for exponent function}
\begin{equation}
  \begin{gathered}
    y = e^{3x} \\
    y = e^u \\
    u = 3x \\
    \frac{dy}{dx} = \frac{dy}{du} * \frac{du}{dx} \\
    \frac{d}{du} e^u = e^u \\
    \frac{d}{dx} 3x = 3 \\
    \frac{dy}{dx} = e^u * 3 = 3e^u = 3e^{3x}
  \end{gathered}
\end{equation}

\subsection{Derivative of the (natural) logarithm}
For natural logarithm:
\begin{equation}
  \frac{d}{dx}(\ln x) = \frac{1}{x}
\end{equation}

For general logarithm:
\begin{equation}
  \frac{d}{dx}(\log_a x) = \frac{1}{x\ln a}
\end{equation}

Example with changing base:
\begin{equation}
  \begin{gathered}
  \log_ax = \frac{\ln x}{\ln a}
  \frac{d}{dx}(\log_ax) = \frac{d}{dx}(\frac{\ln x}{\ln a}) =
  = \frac{1}{\ln a} * \frac{d}{dx}(\ln x) =
  = \frac{1}{\ln a} * \frac{1}{x} = \frac{1}{x\ln a}
  \end{gathered}
\end{equation}
\subsection{Chain rule for logarithmic function}
\begin{equation}
  \begin{gathered}
  y = \ln(2x+1)
  y = \ln u
  u = 2x+1
  y' = \frac{1}{u}
  u' = 2
  \frac{dy}{dx} = \frac{1}{u} * 2 = \frac{2}{u} = \frac{2}{2x+1}
  \end{gathered}
\end{equation}

\section{Integrals}
Also called \textit{antiderivatives}. To represent integrals we use an integral
symbol.

For example:

\begin{equation}
  \int 2x dx = x^2 + C
\end{equation}

Integrals like this are called 'indefinite integrals' and (in this case)
function being integrated is called an 'integrand'.

@@

Power rule for differentiation in reverse:
\begin{equation}
  \frac{d}{dx}(x^{n+1}) = (n+1)x^n
\end{equation}
same as:
\begin{equation}
  \int x^ndx = \frac{x^{n+1}}{n+1}
\end{equation}

Note: power rule does not work if $n=-1$
